---
title: "Covid 19 Syntetic Data - Corona Science, CodeVsCovid Hackathon"
output: html_notebook
author: "Federico Saltarin"
---

First, as always, we import all the libraries

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(tcltk)
```

Here we define all the variables needed later, like how many days and users, which symptoms and so on...

```{r}
days = 20

users = 1000

rows = days * users

first_day = "2019-04-01"

max_family_members = 5

#canton_list = c("ZH","BE","LU","UR","SZ","OW","NW","GL","ZG","FR","SO",
#               "SH","AI","SG","GR","AG","TG","TI","VD","VS","NE","GE","JU")

symptoms = c("coughing", "sneezing", "throat_pain", "fatigue", "breathing_impaired", "headache", "diarrhea", "nausea", "loss_of_smell")

social_data = c("thinks_sick", "close_infected", "usually_home", "contacted_hospital", "tested", "positive_to_test", "risk", "works_in_health", "smoker")

#generate a list of days
day_gen = rep(seq(as.Date(first_day), length.out = days, by = "1 day"),length(n))

#generate the usernames like user1, user2.... usern
n=seq(1:users)
user="user"
user_paste = paste0(user,n)
username = rep(user_paste,each=length(unique(day_gen)))

age_range = seq(10:100)

genders = c("M","F")

user_nationality = "Swiss"

user_country = "Switzerland"

canton_list = c("ZH","BE","LU","TI")

symptom_bool = c(TRUE, FALSE)

family_members = c(1:max_family_members)

symp_severity = c(0,1,2,3)

temp = c(36:40)

r_v_list=c()

output_file = "/home/user/Desktop/Covid_Data.csv"
```

First we open a dataframe from a CSV with defined column fields (I think it's easier to set the needed columns in a spreadsheet first and work on data in here).
And we create a new dataframe with the same column number/names and with the defined number of rows (see variables)
```{r}
df <- read.csv(tk_choose.files(caption = "Select data file: "))
df2 <- data.frame(matrix(ncol = length(colnames(df)), nrow = rows))
colnames(df2) <- colnames(df)
```
Then we can already fill with the days, user, age and gender (random generator for age and gender)
```{r}
df2 = df2 %>% mutate(day = day_gen,
                     user = username) %>% 
              group_by(user) %>% 
              mutate(age = sample(age_range, 1, replace=TRUE),
                     gender = sample(genders, 1, replace=TRUE))
```

Here we ungroup the data and fill with nationality and country (fixed for everyone in our case)
```{r}
df2 = df2 %>% ungroup() %>% 
              mutate(country= user_country,
                     nationality = user_nationality)
```

Then we group by user and fill with canton and family members (random generator)
```{r}
df2 = df2 %>% group_by(user) %>% 
              mutate(canton = sample(canton_list, 1, replace=TRUE),
                     family = sample(family_members, 1, replace=TRUE)) 

```

With the for loop we loop through the social fields (defined before) and randomly generate TRUE or FALSE values
```{r}
for(i in 1:length(social_data)){
  r=sample(c(TRUE,FALSE), length(unique(df2$user)), replace=TRUE)
  rand_vector = rep(r, each = days)
  df2[,social_data[i]] = rand_vector
}
```

Here we generate random temperature values based on normal distribution and correct for values < 36 or > 40
```{r}
df2 = df2 %>% group_by(user) %>% 
  mutate(temp_rand = sample(temp, 1, replace=TRUE),
         temperature = round(rnorm(days,temp_rand, 2),digits=1),
         temperature = ifelse (temperature < 36, 36, temperature),
         temperature = ifelse (temperature > 40, 40, temperature)) 
```

With this other for loop we loop through the symptoms fields (defined before) and randomly generate TRUE or FALSE values
```{r}
df2 = df2 %>% ungroup() 
for(i in 1:length(symptoms)){
  rand_vector=c()
  for (j in 1:length(df2$user)){
    r=sample(c(0:3), 1, replace=TRUE)
    rand_vector=c(rand_vector,r)
  }
  df2[,symptoms[i]] = rand_vector
  }
```
Then we exclude temp_rand that was needed only for calculation of temperature column
```{r}
df2 = df2 %>%
  select(-c(temp_rand))
```

The data are ready and we save them in a CSV file in the location defined before
```{r}
write.csv(df2, output_file)
```









